My title

### 2024-09-23 paper/paper.qmd
Added onto data in the papaer, as well as the introduction, added replications of paper's graphs in relications

@@

The data comes from OpedData Toronto, an open source portal containng datasets carried out at the municipal level (@opendata). This particular dataset is called Street Tree Data, and focuses on city-owned trees located on roads. This information would be most likely used by city planners and road maintenance, ensuring snow plows and street dusters don't impede on any trees that line the roads. It is important to not that there may be some privately owned trees listed among the municipal trees, as they may be of interest with regards to road maintenance or other city services.

>>>>

One way cities have incorportated trees into the city are roadside trees. Trees line many of the cities highways, arterials, collectors, and small roads. Large quantaties of trees lined against highways can act as a natural sound barrier, INSERT STATISTIC WITH SORUCE HERE. Even in cases where trees are more sporadic, they act as

@@

The data comes from OpenData Toronto, an open source portal containng datasets carried out at the municipal level (@opendata). This particular dataset is called Street Tree Data, and focuses on city-owned trees located on roads. This information would be most likely used by city planners and road maintenance, ensuring snow plows and street dusters don't impede on any trees that line the roads. It is important to note that there may be some privately owned trees listed among the municipal trees, as they may be of interest with regards to road maintenance or other city services.

Street Tree Data contains around 32000 observations, each observation being an individual tree. Each observation has a general id for data analysis, as well as an structure id, telling us if the tree is part of an existing structure or building. Next is the location of the tree, using the nearest parcel delivery address, nearest cross-junction, and which ward it is located in. Street Tree contains both the botanical name and the common english name, however we have decided to use only the botanical name to avoid confusion between similar sounding trees. Common english names will be provided for species of key interest. Finally, there is a measurement called dbh_trunk. This is a standard method for measuring the diameter of a tree. The method asks record takeres to read the circumference of the tree from 1.3m off the ground it is rooted in. This measurement has been known to be vaguage, especially when it comes to wawrped or tipping trees, making the exact measurements made on each tree inaccurate at best.
